Dynein notes

### 2017-11-07 reorganize/papers/notes/notes.tex
Add two new papers to notes.tex.

\section{Papers}
\subsection{Paper on our model stepping in the proper direction given our angle scheme}
Figure 7 of 'Three-dimensional structure of cytoplasmic dynein bound to microtubules' shows a cartoon interpretation of a dynein-MT crystal structure indicating that a model which has its tail-load towards the + end will step towards the - end of the MT.\\

>>>>

\section{Papers}
\subsection{Native dynein cryo-EM structure}
Full structure of dynein.\\

\subsection{HC dimerization}
The structure of the dynactin complex and its interaction with dynein -- stuff about HC dimerization, NOT structure\\

Structure of dynactin-dynein. Paper says that ct is pretty loose; loose enough that the angle can rotate 180 to take on the in-vivo state (originally the two motors are 180 degrees apart, but rotate to be parallel). It seems that there is only one dimerization domain at the very N-term of the heavy chain (1-178).\\

Paper says that dynactin may work by separating the two HCs, allowing them to take on an active, bipedal legs-unlocked conformation. Perhaps without this, the two HC legs wrap around each other, or somethign.\\

\subsection{Paper on our model stepping in the proper direction given our angle scheme}
Figure 7 of 'Three-dimensional structure of cytoplasmic dynein bound to microtubules' shows a cartoon interpretation of a dynein-MT crystal structure indicating that a model which has its tail-load towards the + end will step towards the - end of the MT.\\
